---
title       : Developing Data Products Project
subtitle    : Predicting spam
author      : Nicholas Tang
job         : 
framework   : deckjs        # {io2012, html5slides, shower, dzslides, ...}
theme       : mnml
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

We build a prediction model using the spam data as provided by [Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/Spambase)
  
The prediction model is built using caret, with focus on a generalized linear model  
  
We partition the data randomly, using 75% as the training, and 25% as the test/validation set

---

## Code

The following is the code that creates the prediction mode  

```{r, warning=FALSE, message=FALSE,cache=TRUE}
  require(kernlab)
  require(caret)
  require(e1071)
  data(spam)
  set.seed(12345)
  inTrain <- createDataPartition(y=spam$type,p=0.6,list=FALSE)
  training <- spam[inTrain,]
  testing <- spam[-inTrain,]
  fitControl <- trainControl(method="cv", number=10)
  modelFit <- train(type ~., data=training, method="gbm", trControl = fitControl, verbose=FALSE) 

```

---

## Measuring the accuracy

We test the model with our remaining test set
  
```{r, message=F, warning=F, cache=FALSE}

prediction <- predict(modelFit, testing)
prediction_results <- confusionMatrix(prediction, testing$type)
prediction_results$table

```

The out of sample accuracy of our model is **`r prediction_results$overall["Accuracy"]`**

---

## Confusion Matrix

```{r, message=F, warning=F, cache=FALSE}
plot(modelFit)
```

---

## Slide 5


